Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-0mm}}
\def\figcapdown{\vspace{-0mm}}

@@

@@

\extraspacing {\bf Problem $\bm{\mathscr{A}}$.} The input involves a set $P$ of points and set $R$ of rectangles, all in 2D space. In the {\em detection version} of Problem $\mathscr{A}$, the goal is to output, for each point $p \in P$, whether it is covered by at least one rectangle in $R$. Figure~\ref{fig:probs}a gives an example where $P = \set{p_1, p_2, p_3}$ and $R = \set{r_1, r_2}$; the output is ``yes'' for $p_2$ and $p_3$ and ``no'' for $p_1$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time, where $n = |P| + |R|$.

@@

\extraspacing {\bf Problem $\bm{\mathscr{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles, all in 2D space. In the {\em find-lowest} version of the problem, the goal is to report, for each rectangle $r \in R$, its lowest crossing segment $h \in H$. If such an $h$ does not exist, output nothing for $r$.  Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1, h_3), (r_2, h_2)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time where $n = |H| + |R|$.

@@

In the {\em find-all} version of the problem, the goal is to report, for each rectangle $r \in R$, all the segments $h \in H$ crossing $r$. Furthermore, those segments need to be sorted by y-coordinate. Formally, if $h_1, h_2, ..., h_z$ (for some $z \ge 1$) are all the segments in $H$ crossing $r$, we output $(r: h_1, h_2, ..., h_z)$, provided that $y_i \ge y_{i-1}$ for each $i \in [2, z]$ where $y_i$ (resp., $y_{i-1}$) is the y-projection of $h_i$ (resp., $h_{i-1}$). In the example of Figure~\ref{fig:probs}d, the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.

>>>>

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-0mm}}
\def\figcapdown{\vspace{-0mm}}

@@

Let $S$ be a set of segments all of which are either horizontal or vertical. Given a rectangle $r$, we define 
\myeqn{
    \cross_S(r) = \{s \in S \mid \text{$s$ crosses $r$} \}. 
    \label{eqn:cross}
}

@@

\extraspacing {\bf Problem $\bm{\mathscr{A}}$.} The input involves a set $P$ of 2D points and set $R$ of rectangles. In the {\em detection version} of Problem $\mathscr{A}$, the goal is to output, for each point $p \in P$, whether it is covered by at least one rectangle in $R$. Figure~\ref{fig:probs}a gives an example where $P = \set{p_1, p_2, p_3}$ and $R = \set{r_1, r_2}$; the output is ``yes'' for $p_2$ and $p_3$ and ``no'' for $p_1$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time, where $n = |P| + |R|$.

@@

\extraspacing {\bf Problem $\bm{\mathscr{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles, all in 2D space. In the {\em find-lowest} version of the problem, the goal is to report, for each rectangle $r \in R$, the lowest segment in $\cross_H(r)$ (see \eqref{eqn:cross}). If no segment in $H$ crosses $r$, output nothing for $r$.  Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1, h_3), (r_2, h_2)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time where $n = |H| + |R|$.

@@

In the {\em find-all} version of the problem, the goal is to report, for each rectangle $r \in R$, the entire $\cross_H(r)$ sorted by y-coordinate. Formally, if $\cross_H(r) = \set{h_1, h_2, ..., h_z}$ (for some $z \ge 1$), we output $(r: h_1, h_2, ..., h_z)$, provided that $y_i \ge y_{i-1}$ for each $i \in [2, z]$ where $y_i$ (resp., $y_{i-1}$) is the y-projection of $h_i$ (resp., $h_{i-1}$). In the example of Figure~\ref{fig:probs}d, the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.
